---
title: "Evolution of K-pop Girl Group Music"
subtitle: "A Comparative Analysis of Girls' Generation, Twice, and Aespa"
author: 
  - Hanqing Yang
  - Ruiying Li
thanks: "Code and data are available at: [https://github.com/Lorina-Y/SpotifyAPI.git]."
date: today
date-format: long
abstract: "This paper tracing the transformation of Song Styles Across Generations of K-pop, focus on 3 representative girl group: Girls' Generation, Twice, and Aespa"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(spotifyr)
library(ggplot2)
library(lubridate)
library(dplyr)


twice <- readRDS("../data/01-raw_data/twice.rds")
aespa <- readRDS("../data/01-raw_data/aespa.rds")
girlsgeneration <- readRDS("../data/01-raw_data/girlsgeneration.rds")

```


# Introduction
This paper explores the key aspect of this evolution: changes in musical style.
We aim to examine the change of K-pop girls’ band music by analyzing three musical characteristics: valence (emotional positivity), energy (intensity and activity) and danceability (how suitable a track is for dancing).
Through these analyse, this study will offer a comprehensive view of how K-pop girl group music has evolved in music style, providing a deeper understanding of their genre's development.

# Data {#sec-data}
## Overview
This study utilizes data from the Spotify API through the spotifyr package [@spotifyr], which provides detailed audio features for songs by K-pop girl groups. The primary groups analyzed are Aespa, Girls’ generation and Twice, and analyzing and graphing data by using R code [@citeR] and ggplot[@gg2]
 
The origin dataset has 39 variables in total, and this paper only interested in the following 5 variables:artist name,album release date,valence as a measure of the musical positivenes, energy that indicates the intensity,and danceability that reflects how suitable a track is for dancing.
Through this data, the study aims to analyze musical trends over time and assess the international influence of these K-pop girl groups.  

## Change Trends in Audio Features:

Looking at the valence plot(@fig-valence),From 2008 to 2010, there was a noticeable increase in valence for Girls' Generation, indicating a trend towards more positive and upbeat songs. However, after 2013, a decline in valence suggests a shift towards darker or more emotionally complex music. By 2023, Aespa's songs show a renewed rise in valence. This "rise, fall, rise" pattern over the past 20 years reflects an evolving approach to song styles.

The plot(@fig-energy) shows that K-pop girl group songs consistently exhibit high energy,regardless of the release period. Girls' Generation consistently maintains high energy levels, indicating a preference for intense and dynamic tracks. Twice displays more variability, suggesting a mix of high-energy songs alongside more varied styles. In contrast, Aespa's songs show a slight reduction in energy, which could be attributed to stylistic choices rather than an overall shift in K-pop trends. Overall, the consistently high energy reflects a genre-wide emphasis on lively and impactful music, characteristic of K-pop girl group performances.

The danceability data(@fig-danceability) indicates a rising trend in K-pop girl group music from 2008 to 2024. Girls' Generation's songs exhibit lower danceability, while Twice and Aespa show higher levels, reflecting an increased emphasis on dance-oriented tracks in more recent years. This trend suggests K-pop girl groups have placed a greater focus on producing music that is more suitable for choreography and dance performances.

# Conclusion:
These trends suggest that while high energy remains a staple, newer groups emphasize danceability and varied emotional tones, adapting to changing industry trends and audience preferences.

# appendix:

```{r}
#| label: fig-valence
#| fig-cap: Compare the valence of song
#| echo: false
#| warning: false
#| message: false
# Combine the datasets for Girls' Generation, Twice, and Aespa
all_data <- rbind(twice, aespa, girlsgeneration) |>
  mutate(album_release_date = ymd(album_release_date))


valence_plot <- all_data |>
  select(artist_name, album_release_date, valence) |>
  mutate(album_release_date = ymd(album_release_date)) |> 
  ggplot(aes( x = album_release_date, y = valence, color = artist_name)) +
  geom_point(alpha = 0.3) +
  geom_smooth() +
  theme_minimal() +
  facet_wrap(facets = vars(artist_name), dir = "v") +
  labs(
    x = "Album release date",
    y = "Valence",
    color = "Artist",
    title = "Valence Over Time"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

valence_plot

```

```{r}
#| label: fig-energy
#| fig-cap: Compare Energy of the song
#| echo: false
#| warning: false
#| message: false

energy_plot <- all_data |>
  select(artist_name, album_release_date, energy) |>
  ggplot(aes(x = album_release_date, y = energy, color = artist_name)) +
  geom_point(alpha = 0.3) +
  geom_smooth() +
  theme_minimal() +
  facet_wrap(facets = vars(artist_name), dir = "v") +
  labs(
    x = "Album release date",
    y = "Energy",
    color = "Artist",
    title = "Energy Over Time"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
energy_plot
```

```{r}
#| label: fig-danceability
#| fig-cap: Compare danceability of the song
#| echo: false
#| warning: false
#| message: false
# Plot danceability over time
danceability_plot <- all_data |>
  select(artist_name, album_release_date, danceability) |>
  ggplot(aes(x = album_release_date, y = danceability, color = artist_name)) +
  geom_point(alpha = 0.3) +
  geom_smooth(se = FALSE) +
  theme_minimal() +
  facet_wrap(facets = vars(artist_name), dir = "v") +
  labs(
    title = "Danceability Over Time",
    x = "Album Release Date",
    y = "Danceability",
    color = "Artist",
    subtitle = "Comparison of Danceability Trends for Girls' Generation, Twice, and Aespa"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

# Display the plot
danceability_plot


```

\newpage
# References
@citeR
@spotifyr
@rohan
@gg2
@tibble

